Measuring contrast processing in the visual system using SSVEP

### 2024-04-24 review.qmd
Added some stuff on attention

Attention exerts a profound influence on performance: Allowing people to attend covertly to a spatial location for example, improves their performance on a target detection task significantly (Posner, https://pubmed.ncbi.nlm.nih.gov/11934448/, https://pubmed.ncbi.nlm.nih.gov/10788636/,  (Morrone, Denti, & Spinelli,
2004; Pestelli, Ling, & Carrasco, 2009) ). In principle, this effect may be driven both by modulation of the underlying signal or by additional decision-theoretic factors such as reduction in spatial uncertainty (https://jov.arvojournals.org/article.aspx?articleid=2121966, https://jov.arvojournals.org/article.aspx?articleid=2192826). Early experiments with non-human primates showed little evidence for attentionally-driven changes in neuronal spike rates (Luck,
Chelazzi, Hillyard, & Desimone, 1997; Marcus & van
Essen, 2002; McAdams & Maunsell, 1999, Mehta, Ulbert, and
Schroeder (2000)), but with the advent of spatially-resolved human brain imaging methods in the late 90s it became apparent that spatial attention was linked to frank changes in both fMRI bold responses (Tootell, 98: (Brefczynski &
De Yoe, 1999; Buracas & Boynton, 2007; Gandhi,
Heeger, & Boynton, 1999; Kastner, Pinsk, De Weerd,
Desimone, & Ungerleider, 1999; Li, Lu, Tjan, Dosher, &
Chu, 2008; Murray, 2008; Silver, Ress, & Heeger, 2007;
Somers, Dale, Seiffert, & Tootell, 1999; Tootell et al.,
1998),) and EEG signals (https://pubmed.ncbi.nlm.nih.gov/16221931/).

>>>>

Attention exerts a profound influence on visual performance: For example, allowing people to attend covertly to a spatial location for example, improves their performance on a target detection task significantly (Posner, https://pubmed.ncbi.nlm.nih.gov/11934448/, https://pubmed.ncbi.nlm.nih.gov/10788636/,  (Morrone, Denti, & Spinelli,
2004; Pestelli, Ling, & Carrasco, 2009) ). In principle, this effect may be driven both by modulation of the underlying signal or by additional decision-theoretic factors such as reduction in spatial uncertainty (https://jov.arvojournals.org/article.aspx?articleid=2121966, https://jov.arvojournals.org/article.aspx?articleid=2192826). Early experiments with non-human primates showed little evidence for attentionally-driven changes in neuronal spike rates (Luck,
Chelazzi, Hillyard, & Desimone, 1997; Marcus & van
Essen, 2002; McAdams & Maunsell, 1999, Mehta, Ulbert, and
Schroeder (2000)), but with the advent of spatially-resolved human brain imaging methods in the late 90s it became apparent that spatial attention was linked to frank changes in both fMRI bold responses (Tootell, 98: (Brefczynski &
De Yoe, 1999; Buracas & Boynton, 2007; Gandhi,
Heeger, & Boynton, 1999; Kastner, Pinsk, De Weerd,
Desimone, & Ungerleider, 1999; Li, Lu, Tjan, Dosher, &
Chu, 2008; Murray, 2008; Silver, Ress, & Heeger, 2007;
Somers, Dale, Seiffert, & Tootell, 1999; Tootell et al.,
1998),) and EEG signals (https://pubmed.ncbi.nlm.nih.gov/16221931/).
